Chronic conditions and increased antibiotic consumption

### 2017-03-30 chronic-conditions/chronic-condition-drivers.Rmd
chronic conditions, aggregate

multivariate_res = usage %>%
  select(n_claims, age, is_female, AMI:HYPOTH) %>%
  glm(multivariate_formula, data=., family='poisson') %>%
  tidy
```

@@

```{r show_multivariate, cache=FALSE}
# Here I need to do some fancy footwork to get the condition names in
# The terms look like (Intercept), age, is_female, AMITRUE, COPDTRUE, etc.
# So chop off TRUE where it is, then match with the known names, and
# keep the (Intercept), etc. if it didn't match

multivariate_res %>%
  mutate(pct.increase=round((exp(estimate)-1.0)*100)) %>%
  mutate(condition=str_replace(term, 'TRUE$', '')) %>%
  left_join(condition_names, by='condition') %>%
  mutate(term=if_else(is.na(condition_name), condition, condition_name)) %>%
  select(term, pct.increase, estimate, p.value) %>%
  arrange(desc(abs(estimate))) %>%
  kable
```

@@

### Negative binomial

The claims data are distributed more like a negative binomial than a Poisson (i.e., the variance in counts exceeds the mean). Negative binomial regressions give similar results to the Poisson results. For example, the COPD coefficient is 0.811 (vs. 0.806) and the rheumatoid arthritis coefficient is 0.466 (vs. 0.465).

```{r negative_binomial}
usage %>%
  mutate(age=age-65) %>%
  MASS::glm.nb(n_claims ~ age + is_female + COPD, data=.) %>%
  broom::tidy %>%
  select(term, estimate)
```

>>>>

multivariate_res = usage %>%
  select(n_claims, age, is_female, AMI:HYPOTH) %>%
  glm(multivariate_formula, data=., family='poisson') %>%
  broom::tidy()
```

```{r multivariate_negbin}
multivariate_negbin_res = usage %>%
  MASS::glm.nb(multivariate_formula, data=.) %>%
  broom::tidy()
```

@@

```{r show_multivariate, cache=FALSE}
# Here I need to do some fancy footwork to get the condition names in
# The terms look like (Intercept), age, is_female, AMITRUE, COPDTRUE, etc.
# So chop off TRUE where it is, then match with the known names, and
# keep the (Intercept), etc. if it didn't match
multivariate_res %>%
  mutate(pct.increase=round((exp(estimate)-1.0)*100)) %>%
  mutate(condition=str_replace(term, 'TRUE$', '')) %>%
  left_join(condition_names, by='condition') %>%
  mutate(term=if_else(is.na(condition_name), condition, condition_name)) %>%
  select(term, pct.increase, estimate, p.value) %>%
  arrange(desc(abs(estimate))) %>%
  kable
```

#### Comparison to negative binomial

The negative binomial model gave almost exactly the same results. Here I show a plot comparing the coefficients estimates the two models. The one point that's deviated from the line is the intercept, which isn't comparable between the two models anyhow. Notably, the Poisson model appears to slightly underestimates the coefficients.

```{r compare_poisson_negbin}
bind_rows(mutate(multivariate_res, method='Poisson'),
          mutate(multivariate_negbin_res, method='negbin')) %>%
  mutate(condition=str_replace(term, 'TRUE$', '')) %>%
  left_join(condition_names, by='condition') %>%
  mutate(term=if_else(is.na(condition_name), condition, condition_name)) %>%
  select(term, method, estimate) %>%
  spread(method, estimate) %>%
  ggplot(aes(x=Poisson, y=negbin)) +
  geom_point() +
  geom_abline() +
  xlim(-0.2, 0.6) +
  xlab('Poisson multivariate model coefficient') + ylab('negative binomial multivariate model coefficient') +
  theme_minimal()
```

@@
